---
title: "syntR Tutorial"
author: "Kate Ostevik and Kieran Samuk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r read_map}

devtools::install_github("ksamuk/syntR")

# load the map
data(ann_pet_map)

# read in list of chromosome lengths for map1
data(ann_chr_lengths)

# put all the chromosomes on one scale
map_list <- make_one_map(ann_pet_map, map1_max_chr_lengths = ann_chr_lengths)

```


```{r plot_map}
# plot map
plot_maps(map_df = map_list[[1]], map1_chrom_breaks = map_list[[2]], map2_chrom_breaks = map_list[[3]])

```

```{r reorder_map}
# reorder and flip some chromosomes
map2_chr_order <- c("Pet8", "Pet9", "Pet12_16", "Pet15", "Pet16_17", "Pet17")
flip_chrs <- c("Pet9")
map_list <- make_one_map(map, map1_max_chr_lengths = map1_chr_lengths, map2_chr_order = map2_chr_order, flip_chrs = flip_chrs)
plot_maps(map_df = map_list[[1]], map1_chrom_breaks = map_list[[2]], map2_chrom_breaks = map_list[[3]])

```

```{r find_params}
# find best parameter combination
# run find_synteny_blocks with each parameter combination and collect summary statistics
parameter_data <- test_parameters(map_list, max_cluster_range_list = seq(1, 5, by = 0.5), max_nn_dist_list = seq(10, 50, by = 10))
plot_summary_stats(parameter_data[[1]], "composite")
# pick max_cluster_range = 2 and max_nn_dist = 10

```

```{r find_blocks}
# find synteny blocks
map_all_dfs <- find_synteny_blocks(map_list, max_cluster_range = 2, max_nn_dist = 10, plots = TRUE)
map_all_dfs[[2]]
map_all_dfs[[5]]

# plot synteny block orientations
map_all_dfs[[1]] %>%
    plot_maps(map_list[[2]], map_list[[3]], col = c("blue", "grey", "red", "black")[as.numeric(as.factor(.$orientation))], 
              main = "Synteny block orientation",  cex_val = 0.75)

```


  

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
